InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
Changed GPT to GPT2

The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models. Its is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set. This data set leverages strict filtering and stringent deduplication to uplift the quality of web data. \cite{penedo2023refinedweb}

>>>>

We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.

\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
\begin{enumerate}
	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
	\item Discriminative fine-tuning on every specific task.
\end{enumerate}

To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
